---
title: "Untitled"
author: "Jasen"
date: "2024-07-05"
output: pdf_document
---

```{r}
library(devtools)
```

```{r}
# use_git()
```

# look to edit the function

```{r}
# use_r("strsplit1")
```
# load the functions but they aren't in the global environment

```{r}
load_all()
```

```{r}
x <- "alfa,bravo,charlie,delta"
strsplit1(x, split = ",")

exists("strsplit1", where = globalenv(), inherits = FALSE)
```
# checking that things still work

```{r}
check()
```

```{r}
use_mit_license()
```

```{r}
document()
```

```{r}
?strsplit1
```

```{r}
check()
```

```{r}
install()
```

```{r}
library(regexcite)

x <- "alfa,bravo,charlie,delta"
strsplit1(x, split = ",")
```
# This initializes the unit testing machinery for your package.

```{r}
use_testthat()
```

# now we load the test cases

```{r}
use_test('strsplit1')
```

# and then we see if the tests have passed

```{r}
test()
```
# how to use other packages when making your packages

```{r}
use_package("stringr")
```
# reshuffles the names

# we only rename "strsplit1" as "str_split_one"
# the contents are the same 

```{r}
rename_files("strsplit1", "str_split_one")
```

# update the test cases

```{r}
use_testthat()
use_test('str_split_one')
```
# also need to update the NAMESPACE

```{r}
document()
```

# try the function again

```{r}
load_all()

str_split_one("a, b, c", pattern = ", ")
```
# upload to github

```{r}
use_github()
```
